Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2018-10-05 analysis/paper/paper.Rmd
Renamed data_retrieval script for clarity; introduced switch for data access commands based on who is knitting markdown file; after investigation, decided better to input data from CSV files; added recommendation text to update data management workflow.

@@

### Survey Design 
Species: 
Targets: loons, grebes, cormorants, herons, ducks, geese, plovers, sandpipers, gull, alcids, [kingfishers]
Questions: clarify role of kingfishers.

>>>>

library(dply);library(ggplot2);library(dbplyr);

@@

### Survey Design

```{r DataInput, eval=TRUE, echo=FALSE, cache=TRUE}
if (system("git config user.email")=="mward2@swarthmore.edu") source("./scripts/data_retrievalSwarthmore.R")
else source("./scripts/data_retrievalNPS.R")

Species: 
Targets: loons, grebes, cormorants, herons, ducks, geese, plovers, sandpipers, gull, alcids, [kingfishers]
Questions: clarify role of kingfishers.
